SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-20 paper/encoding.tex

\begin{df}
  A VTS $G$ is tuple $(\nodes,\mols,\edges,\nlabel,\pair,\edgef,\nodef)$, where
  \begin{itemize}
  \item $\nodes$ is a set of nodes representing compartments in the VTS,
  \item $\mols$ is the set of molecules flowing in the network, 
  \item $\nlabel : \nodes \maps \powerset{\mols}$ defines the molecules present in the nodes  
  \item $ \nodes \times \powerset{\mols} \times \nodes \subseteq \edges$ is the set of edges
    with molecule sets as labels
  \item $\pair : \mols \times \mols$ is pairing relating
  \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes
  \item $\edgef : \mols \maps \powerset{\mols} \maps \booleans $ is activity maps for edges
  \end{itemize}
\end{df}
$\pair$, $\nodef$, and $\edgef$ defines activity of a molecule on nodes and edges.
A molecule $k$ is {\em active} at node $n$ if $\nodef(k,\nlabel(n))$ is true.
A molecule $k$ is {\em active} at edges $(n,M',n')$ if $\edgef(k,M')$ is true.

Variants of the model : restrictions...

formal definition of the properties in the terms of VTS.

>>>>

\begin{df}
  A VTS $G$ is tuple $(\nodes,\mols,\edges,\nlabel,\pair,\edgef,\nodef)$, where
  \begin{itemize}
  \item $\nodes$ is a set of nodes representing compartments in the VTS,
  \item $\mols$ is the set of molecules flowing in the network, 
  \item $\nlabel : \nodes \maps \powerset{\mols}$ defines the molecules present in the nodes  
  \item $ \nodes \times (\powerset{\mols}-\emptyset) \times \nodes \subseteq \edges$ is the set of edges
    with molecule sets as labels
  \item $\pair : \mols \times \mols$ is pairing relating
  \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes
  \item $\edgef : \mols \maps \powerset{\mols} \maps \booleans $ is activity maps for edges
  \end{itemize}
\end{df}
$\pair$ defines which molecules can fuse with which molecules. 
$\nodef$ and $\edgef$ are used to define activity of molecules on nodes and edges.
A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and $\nodef(k,\nlabel(n))$ is true.
A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and $\edgef(k,M')$ is true.

We will also consider several variations of the model.
%
For example, unique edge between two nodes, activity of molecules is not constrained by
$\nodef$ and $\edgef$, and \ashu{other variations?}.
%

A {\em path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
such that $(n_i,\_,n_{i+1}) \in \edges$ for each $ 0 < i < \ell$.
%
For a molecule $m \in M$,
An {\em $m$-path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
such that $(n_i,M',n_{i+1}) \in \edges$ and $m \in M'$ for
each $ 0 < i < \ell$.
%
A node $n'$ is {\em reachable} from node $n$ in $G$ if there is a path
$n,...,n'$ in $G$.
%
A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
$m$-path $n,...,n'$ in $G$.
%
We call $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
$n$ is $m$-reachable from $n'$.
%
We call $G$ {\em connected} if for each $n,n' \in \nodes$,
$n'$ is reachable from $n$ in $G$.
%
We call $G$ $k$-connected if for each $E' \subseteq \edges$ and $|E'| < k$,
$(\nodes,\mols,\edges-E',\nlabel,\pair,\edgef,\nodef)$ is connected.
%
An edge $(n,M',n') \in \edges$ {\em fuses} with its destination node $n'$
if

### 2017-06-20 paper/experiments.tex

%
$\zthree$ was able to solve the constraints up to 10
nodes.
%

In table~\ref{tbl:qf-results} 
\b PARTIAL ...

\begin{table}[!ht]
\centering
\def\arraystretch{1.6}
\caption{
{\bf Activity regulation of molecules and corresponding connectivity of the graph.}}
  \begin{tabular}{|c|l|l|c|c|}
    \hline
  \multirow{2}{*}{\textbf{Sr.No}}  & \multicolumn{2}{c|}{\textbf{Activity mechanism}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-5}
    {} & \multirow{1}{*} {\bf{ On compartment}} & \multirow{1}{*} {\bf{On vesicle}}  & \textbf{\textbf{Least}} & \textbf{Highest}\\
    %\hhline{~--}
    \hline
E. & Boolean function & Boolean function & 2-connected & 3-connected \\ \hline
C. & None & Boolean function & 3-connected & 3-connected \\  \hline
F. & Boolean function & Pairing inhibition & 4-connected & 4-connected \\ \hline
D. & None & Pairing inhibition & No graph & No graph \\ \hline
B. & Boolean function & None & No graph & No graph \\ \hline
A. & None & None & No graph & No graph \\ \hline
G. & Boolean function & Every edge is distict & 3-connected & 3-connected \\ \hline
H. & Self edges are allowed & Boolean funcion & No-idea & No-idea \\ \hline

  \end{tabular}
\label{table1}
\end{table}

>>>>

%
$\zthree$ was able to solve the constraints up to 15
nodes.
%

In table~\ref{tbl:qf-results}

\begin{table}[!ht]
\centering
\def\arraystretch{1.6}
\caption{
{\bf Activity regulation of molecules and corresponding connectivity of the graph.}}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
  \multirow{2}{*}{\textbf{Sr.No}}  & \multicolumn{2}{c|}{\textbf{Activity constraint}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-5}
    {} & \multirow{1}{*} {\bf{ On compartment}} & \multirow{1}{*} {\bf{On vesicle}}  & \textbf{\textbf{Least}} & \textbf{Highest}\\
    %\hhline{~--}
    \hline
E. & A\_nb & A\_eb & 2-connected & 3-connected \\ \hline
C. & A\_nn & A\_eb & 3-connected & 3-connected \\  \hline
F. & A\_nb & A\_ep & 4-connected & 4-connected \\ \hline
D. & A\_nn & A\_ep & No graph & No graph \\ \hline
B. & A\_nb & A\_en & No graph & No graph \\ \hline
A. & A\_nn & A\_en & No graph & No graph \\ \hline
G. & A\_nb & A\_eb + C\_ed & 3-connected & 3-connected \\ \hline
H. & A\_nb & A\_eb + C\_es & No-idea & No-idea \\ \hline

% C_es :Self edges are allowed
% C_ed : Every edge is distinct 
  \end{tabular}
\label{table1}
\end{table}
